---
title: "Project 2"
author: "Group 16"
date: "2022/3/8"
output:
  pdf_document:
    latex_engine: pdflatex
    number_sections: yes
    keep_tex: true
  html_document:
    df_print: paged
fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA, message = FALSE, warning = FALSE)
```

```{r libraries}
library(tidyverse)
library(ggplot2)
library(skimr)
library(GGally)
library(olsrr)
library(kableExtra)
library(moderndive)
library(lme4)
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library(janitor)
```

```{r load data}
data <- read.csv("dataset16.csv",encoding = "UTF-8")
```

```{r data summary and drop NAs}
skim(data)
#price column have NAs with complete_rate 0.923, so we can simply drop rows with NAs.
data_without_NAs <- data %>% 
  drop_na() %>% 
  mutate(above90 = ifelse(points > 90, 1, 0))
skim(data_without_NAs)
```

```{r visual summary for numeric}
# data_without_NAs %>% 
#   ggplot(mapping = aes(y = points)) +
#   geom_boxplot()
# 
# data_without_NAs %>% 
#   ggplot(mapping = aes(y = price)) +
#   geom_boxplot()
#Many outliers

# data_without_NAs %>% 
#   ggplot(mapping = aes(x = country, y = points)) +
#   geom_boxplot()
# 
# data_without_NAs %>% 
#   ggplot(mapping = aes(x = country, y = price)) +
#   geom_boxplot()

data_without_NAs %>% 
  ggplot(mapping = aes(x = above90, y = price, group = above90)) +
  geom_boxplot()



```

```{r catigrical data}
data_without_NAs=tidyr::unite(data_without_NAs,'country_p',country,province,remove = FALSE)
data_without_NAs$country <- as.factor(data_without_NAs$country)
data_without_NAs$above90<-as.factor(data_without_NAs$above90)
levels(data_without_NAs$above90) <- c("Low", "High")
data_without_NAs$title <- as.factor(data_without_NAs$title)
data_without_NAs$variety<-as.factor(data_without_NAs$variety)
data_without_NAs$winery<-as.factor(data_without_NAs$winery)
data_without_NAs$country_p<-as.factor(data_without_NAs$country_p)
data_without_NAs$province<-as.factor(data_without_NAs$province)
```

```{r boxplot for country}
ggplot(data = data_without_NAs, aes(x = above90, y = price, fill = above90)) +
geom_boxplot() +
labs(x = "Points", y = "Price") +
theme(legend.position = "none")
```


```{r country points stats}
data_without_NAs %>%
tabyl(country, above90) %>%
adorn_percentages() %>%
adorn_pct_formatting() %>%
adorn_ns() # To show original counts
```



```{r country points graph}
ggplot(data = data_without_NAs, aes(x = above90, group = country)) +
geom_bar(aes(y = ..prop.., fill = country), stat = "count", position = "dodge") +
labs(x = "Points", y = "Proportion")

```

* country – Country of origin
* points – The number of points awarded for the wine on a scale of 1-100 (although reviews are only posted for ratings 80 and above)
* price – The cost for a bottle of wine
* province – The province or state the wine is from
* title – The title of the wine review
* variety – The type of grape
* winery – The winery that made the wine

* country – Categorical, could be influential
* points – Numerical, response, split in to above and below 90 and become binary
* price – Numerical, could be influential
* province – Categorical, could be influential
* title – useless for model
* variety – Categorical, could be influential
* winery – Categorical, could be a little bit influential, since have 1500+ unique value, maybe dropped



```{r deduplication}
data_without_NAs %>% 
  group_by(title) %>% 
  count() %>% 
  arrange(desc(n))
#title Cramele Recas 2014 Legendary Estate Series Cabernet Sauvignon (Romania) appear twice
data_without_NAs %>% 
  filter(title == 'Cramele Recas 2014 Legendary Estate Series Cabernet Sauvignon (Romania)')
#two observation(331 and 1807) with same information, we drop it
data_without_NAs <- data_without_NAs %>%
  filter(X != 1807)
```

```{r}
glm(above90 ~ country + province + price + variety + winery, data = data_without_NAs, family = binomial(link = "logit"))
```

```{r}
model_price <- glm(above90 ~ price, data = data_without_NAs, family = binomial(link = "logit"))
summary(model_price)
```


```{r}
model_price_country <- glm(above90 ~ price + country, data = data_without_NAs, family = binomial(link = "logit"))
summary(model_price_country)
```

```{r explore country distribution}
data_without_NAs %>% 
  group_by(country) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count))
```

```{r explore province distribution}
data_without_NAs %>% 
  group_by(province) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count))
```

```{r explore country-province distribution}
data_without_NAs %>% 
  group_by(country, province) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count))
```


```{r winery}
data_without_NAs %>% 
  group_by(winery) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count))

data_without_NAs %>% 
  group_by(winery) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count)) %>% 
  group_by(count) %>% 
  summarize(sumcount = sum(count), High = sum(High), Low = sum(Low))
```
```{r processed_winery}
data_without_NAs %>% 
  group_by(winery) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count)) %>% 
  mutate(processed_winery = if_else(count == 1, "small winerys", "large winerys")) %>% 
  # as.character(winery)
  group_by(processed_winery) %>% 
  summarize(count = sum(count), High = sum(High), Low = sum(Low)) %>% 
  arrange(desc(count)) 
```



```{r}
data_without_NAs %>% 
  group_by(variety) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count))

data_without_NAs %>% 
  group_by(variety) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count)) %>% 
  group_by(count) %>% 
  summarize(sumcount = sum(count), High = sum(High), Low = sum(Low))
```

```{r}
data_without_NAs %>% 
  group_by(variety) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count))

data_without_NAs %>% 
  group_by(variety) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count)) %>% 
  group_by(count) %>% 
  summarize(sumcount = sum(count), High = sum(High), Low = sum(Low))
```



