---
title: "Project 2"
author: "Group 16"
date: "2022/3/8"
output:
  pdf_document:
    latex_engine: pdflatex
    number_sections: yes
    keep_tex: true
  html_document:
    df_print: paged
fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA, message = FALSE, warning = FALSE)
```

```{r libraries}
library(tidyverse)
library(ggplot2)
library(skimr)
library(GGally)
library(olsrr)
library(kableExtra)
library(moderndive)
library(lme4)
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library(janitor)
```

```{r load data}
#data <- read.csv("dataset16.csv")
data<-load("2000data.RData")
```


# Visualization

```{r data summary and drop NAs}
skim(data)
#price column have NAs with complete_rate 0.923, so we can simply drop rows with NAs.
data_without_NAs <- data %>% 
  drop_na() %>% 
  mutate(above90 = ifelse(points > 90, 1, 0))
skim(data_without_NAs)
```

```{r catigrical data}
data_without_NAs=tidyr::unite(data_without_NAs,'country_p',country,province,remove = FALSE)
data_without_NAs$country <- as.factor(data_without_NAs$country)
data_without_NAs$above90<-as.factor(data_without_NAs$above90)
levels(data_without_NAs$above90) <- c("Low", "High")
data_without_NAs$title <- as.factor(data_without_NAs$title)
data_without_NAs$variety<-as.factor(data_without_NAs$variety)
data_without_NAs$winery<-as.factor(data_without_NAs$winery)
data_without_NAs$country_p<-as.factor(data_without_NAs$country_p)
data_without_NAs$province<-as.factor(data_without_NAs$province)
```

```{r boxplot for country}
ggplot(data = data_without_NAs, aes(x = above90, y = price, fill = above90)) +
geom_boxplot() +
labs(x = "Points", y = "Price") +
theme(legend.position = "none")
```


```{r country points stats}
data_without_NAs %>%
tabyl(country, above90) %>%
adorn_percentages() %>%
adorn_pct_formatting() %>%
adorn_ns() # To show original counts
```

```{r}
view=aggregate(data_without_NAs$country_p, by=list(type=data_without_NAs$country),length)
arrange(view,desc(x))
```

```{r country points graph 2}
# this plot might be easier to view than the plot in the chunk above
ggplot(data_without_NAs, aes(x = country, fill = above90)) +
    geom_bar(position = "fill") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "Points", y = "Proportion")

```





# Method
## Area

```{r}
NorthAmerica=filter(data_without_NAs,country=='US'|country=='Canada')
 NorthAmerica=filter(data_without_NAs,country=='US'|country=='Canada')
 NorthAmerica['Area']='NorthAmerica'
 
Italy=filter(data_without_NAs,country=='Italy')
 Italy['Area']='Italy'
 
 France=filter(data_without_NAs,country=='France')
 France['Area']='France'
 
 Spain=filter(data_without_NAs,country=='Spain')
 Spain['Area']='Spain'
 
 SouthAmerica=filter(data_without_NAs,country=='Portugal'|country=='New Zealand'|country=='South Africa'	)
 SouthAmerica['Area']='SouthGlobe'
 
 SouthGlobe=filter(data_without_NAs,country=='Australia'|country=='Chile'|country=='Argentina'	)
 SouthGlobe['Area']='SouthAmerica'
 
 WestEU=filter(data_without_NAs,country=='Austria'|country=='Germany'|country=='England'	)
 WestEU['Area']='WestEU'
 
 India=filter(data_without_NAs,country=='India')
India['Area']='India'
 
 EastEU=filter(data_without_NAs,country=='Greece'|country=='Romania'|country=='Croatia'|country=='Israel'|country=='Bulgaria'|country=='Georgia'|country=='Slovenia'|country=='Turkey'|country=='Uruguay'|country=='Czech Republic'|country=='Hungary')
 EastEU['Area']='EastEU'
 
 data_area=bind_rows(NorthAmerica,Italy,France,Spain,SouthAmerica,SouthGlobe,WestEU,EastEU,India)
```

* country – Categorical, could be influential
* points – Numerical, response, split in to above and below 90 and become binary
* price – Numerical, could be influential
* province – Categorical, could be influential
* title – useless for model
* variety – Categorical, could be influential
* winery – Categorical, could be a little bit influential, since have 1500+ unique value, maybe dropped




```{r}
model_price <- glm(above90 ~ price, data = data_area, family = binomial(link = "logit"))
summary(model_price)
```


```{r explore country-province distribution}
data_area %>% 
  group_by(country, province) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count))
```



## Wineries, varieties 

```{r winery}
data_area %>% 
  group_by(winery) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count)) %>% 
  group_by(count) %>% 
  summarize(sumcount = sum(count), High = sum(High), Low = sum(Low))
```

```{r}
data_area %>% 
  group_by(variety) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count))

data_area %>% 
  group_by(variety) %>% 
  summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count)) %>% 
  group_by(count) %>% 
  summarize(sumcount = sum(count), High = sum(High), Low = sum(Low))%>%
  ggplot(aes(x=count ))+ geom_histogram()
```



```{r}
data_area=data_area %>% 
  mutate(Popularity=ifelse(n() >= 100, "popular", "nonpopular")) %>%
  group_by(winery) %>%
  mutate(processed_winery=ifelse(n() == 1, "small wineries", "large wineries")) 
```


## Year

