---
title: "Research on the main influencing factors of wine score"
author: "Group 16"
date: "2022/3/8"
output:
  pdf_document:
    latex_engine: pdflatex
    number_sections: yes
    keep_tex: true
  html_document:
    df_print: paged
fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA, message = FALSE, warning = FALSE)
```

```{r libraries}
library(tidyverse)
library(ggplot2)
library(skimr)
library(GGally)
library(olsrr)
library(kableExtra)
library(moderndive)
library(lme4)
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
library(janitor)
library(rms)
library(MASS)
library(rcompanion)
library(fastDummies)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(ROCR)
```

```{r load data}
data <- read.csv("dataset16.csv",encoding = "UTF-8")
```

# introduction

Based on a dataset from WineEnthusiast, we will analyze various attributes (origin, price, rating, etc.) of a bottle of wine appearing in the dataset and try to find out the variables that have an impact on whether a wine's rating is greater than 90. GLM models will be used
to compare the influence of each feature on the rating score.

# Data cleaning and EDA

## Data summary and cleaning

According to the requirements of the question, we need to create a new binary variable based on the score of the wine to indicate whether the score of a bottle of wine is greater than 90, which will be used as our response variable.

From the title column, we can filter out the year of manufacture of the wine as a more useful feature


```{r data summary and drop NAs}
data %>% 
  skim()

# Create a new binary variable based on the score of the wine to indicate whether the score of a bottle of wine is greater than 90, which will be used as our response variable.
# Filter out the year of manufacture of the wine from title column
data_processed <- data %>% 
  mutate(above90 = ifelse(points > 90, 1, 0)) %>%  
  mutate(year = unlist(lapply(title,  function (x){str_extract(x, pattern = "\\d\\d\\d\\d")}))) 

data_processed %>% 
  skim()
```

We noticed that the Country and Province column had a missing value, the Price column had 133 missing values, and the year column had 133 missing values, and we found that the title had a duplicate value, which could represent a duplicate piece of data. We found this duplicate and removed it from the dataset.

```{r deduplication}
data_processed %>% 
  group_by(title) %>% 
  count() %>% 
  arrange(desc(n))
#title Cramele Recas 2014 Legendary Estate Series Cabernet Sauvignon (Romania) appear twice

data_processed %>% 
  filter(title == 'Cramele Recas 2014 Legendary Estate Series Cabernet Sauvignon (Romania)')

#two observation(331 and 1807) with same information, we drop the 1807th observation
data_processed <- data_processed %>%
  filter(X != 1807)
```

## Categorical data to factor

Since we plan to analysis with glm, we need transform our categorical variables to factor

```{r process catigrical veriables}
data_processed <- tidyr::unite(data_processed,'country_p',country,province,remove = FALSE)
data_processed$country <- as.factor(data_processed$country)
data_processed$above90 <- as.factor(data_processed$above90)
levels(data_processed$above90) <- c("Low", "High")
data_processed$title <- as.factor(data_processed$title)
data_processed$variety <- as.factor(data_processed$variety)
data_processed$winery <- as.factor(data_processed$winery)
data_processed$country_p <- as.factor(data_processed$country_p)
data_processed$province <- as.factor(data_processed$province)
```

## View data

Here is a summary of our data:

* country – Country of origin; Categorical, could be influential
* points – The number of points awarded for the wine on a scale of 1-100 (although reviews are only posted for ratings 80 and above); Numerical, response, split in to above and below 90 and become binary
* price – The cost for a bottle of wine; Numerical, could be influential
* province – The province or state the wine is from
* title – The title of the wine review; useless for model but we can filter year from it
* variety – The type of grape; Categorical, could be influential
* winery – The winery that made the wine; Categorical, could be a little bit influential, since have 1500+ unique value, maybe dropped or processed.

### View data: general plots.

We can see that the distribution of scores is not centered around 90, in the entire dataset there are more wines with scores below 90 than those above 90, which is a very important fact

```{r Box plot for other variables v.s. points}
data_processed %>%
  ggplot(mapping = aes(y = points)) +
  geom_boxplot()

data_processed %>%
  ggplot(mapping = aes(y = price)) +
  geom_boxplot()
# Many outliers

data_processed %>%
  ggplot(mapping = aes(x = country, y = points)) +
  geom_boxplot()
#not readable

data_processed %>%
  ggplot(mapping = aes(x = country, y = price)) +
  geom_boxplot()
#not readable

data_processed %>% 
  ggplot(mapping = aes(x = above90, y = price, group = above90)) +
  geom_boxplot()
# Many outliers and significant difference

```


### View data: price vs scores
A box-plot is to show the relationship between price and scores.

The result shows an obvious relationship between price and scores.
```{r boxplot for price}
ggplot(data = data_processed, aes(x = above90, y = price, fill = above90)) +
geom_boxplot() +
labs(x = "Points", y = "Price") +
theme(legend.position = "none")
```

### View data: country vs scores
View countries and scores.

The comparison bar plot shows an obvious relations between country and scores.
```{r country points stats}
data_processed %>%
tabyl(country, above90) %>%
adorn_percentages() %>%
adorn_pct_formatting() %>%
adorn_ns() # To show original counts
```

```{r country v.s. points graph 2}
# this plot might be easier to view than the plot in the chunk above
ggplot(data_processed, aes(x = country, fill = above90)) +
    geom_bar(position = "fill") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "Points", y = "Proportion")
```


### View data: Country and province distribution

Specific data table to show the number of different countries, total number of rows of high scores, and low scores.
```{r explore country distribution}
data_processed %>% 
  group_by(country) %>% 
  dplyr::summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count))
```

```{r explore province distribution}
data_processed %>% 
  group_by(province) %>% 
  dplyr::summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count))
```

```{r explore country-province distribution}
data_processed %>% 
  group_by(country, province) %>% 
  dplyr::summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count))
```


### View data: winery distribution

Specific data table to show the number of wineries, total number of rows of high scores, and low scores.

```{r winery}
data_processed %>% 
  group_by(winery) %>% 
  dplyr::summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count)) %>% 
  group_by(count) %>% 
  dplyr::summarize(sumcount = sum(count), High = sum(High), Low = sum(Low))
```
We find the winery only appears once is of large amount. 

Label them 'small wineries' and 'large wineries' to see the distribution.
```{r processed_winery}
data_processed %>% 
  group_by(winery) %>% 
  dplyr::summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count)) %>% 
  mutate(processed_winery = if_else(count == 1, "small wineries", "large wineries")) %>% 
  # as.character(winery)
  group_by(processed_winery) %>% 
  dplyr::summarize(count = sum(count), High = sum(High), Low = sum(Low)) %>% 
  arrange(desc(count)) 
```


### View data: variety distribution
The hist graph shows the number of varieties of wines are distributed with slant and gaps. 
```{r variety distribution}
data_processed %>% 
  group_by(variety) %>% 
  dplyr::summarize(Count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(Count)) %>% 
  ggplot(mapping = aes(x = Count,label=..count..)) +
  geom_histogram(binwidth=20,color="white",breaks = seq(0, 210, 20)) +
  geom_text(stat="bin", size=2,vjust=0,breaks = seq(0, 210, 20),position="stack") +
  labs(x = 'Number of wines' , y = 'Number of varieties')
```


# Method to group levels

Since we have too many levels in categories of country, province, winery and variety, methods of division are applied below.

## Group area

Since the countries have included the information for origin of wines, we will only take countries into consideration. The separated origins are called 'Area'.

The area is divided by geographical region.

NorthAmerica: 'US', 'Canada'

Italy, France, Spain are not combined with any other countries because they have many enough wines.

India is droped because it only has one row.

SouthGlobe: 'Portugal','New Zealand','South Africa'

SouthAmerica: 'Australia', 'Chile', 'Argentina'	

WestEU: 'Austria', 'Germany', 'England'	

EastEU: 'Greece', 'Romania', 'Croatia', 'Israel', 'Bulgaria', 'Georgia', 'Slovenia', 'Turkey', 'Uruguay', 'Czech Republic', 'Hungary'

```{r group country by area}
NorthAmerica=filter(data_processed,country=='US'|country=='Canada')
 NorthAmerica=filter(data_processed,country=='US'|country=='Canada')
 NorthAmerica['Area']='NorthAmerica'
 
Italy=filter(data_processed,country=='Italy')
 Italy['Area']='Italy'
 
 France=filter(data_processed,country=='France')
 France['Area']='France'
 
 Spain=filter(data_processed,country=='Spain')
 Spain['Area']='Spain'
 
 SouthGlobe=filter(data_processed,country=='Portugal'|country=='New Zealand'|country=='South Africa'	)
 SouthGlobe['Area']='SouthGlobe'
 
 SouthAmerica=filter(data_processed,country=='Australia'|country=='Chile'|country=='Argentina'	)
 SouthAmerica['Area']='SouthAmerica'
 
 WestEU=filter(data_processed,country=='Austria'|country=='Germany'|country=='England'	)
 WestEU['Area']='WestEU'
 
# India=filter(data_processed,country=='India')
#India['Area']='India'
 
 EastEU=filter(data_processed,country=='Greece'|country=='Romania'|country=='Croatia'|country=='Israel'|country=='Bulgaria'|country=='Georgia'|country=='Slovenia'|country=='Turkey'|country=='Uruguay'|country=='Czech Republic'|country=='Hungary')
 EastEU['Area']='EastEU'
 
data_area <- bind_rows(NorthAmerica,Italy,France,Spain,SouthAmerica,SouthGlobe,WestEU,EastEU)
```

## Group Wineries

Wineries are separated by the number of wines produced by themselves. 

Large wineries: wineries of more than 1 wines.

Small wineries: wineries of 1 wines.

```{r group wineries by size}
data_area=data_area %>% 
  group_by(winery) %>%
  mutate(processed_winery=ifelse(n() == 1, "small_wineries", "large_wineries")) 
```


## Group varieties

The variety of a wine is divided by whether it is in common_8_wine sets.

Te source is on https://winefolly.com/deep-dive/common-types-of-wine/

common_8: 'Cabernet Sauvignon', 'Syrah', 'Zinfandel', 'Pinot Noir', 'Chardonnay', 'Sauvignon Blanc', 'Pinot Gris', 'Riesling'.

not_common_8: others.
```{r group varieties by common or not}
common_8_wine <- c('Cabernet Sauvignon', 'Syrah', 'Zinfandel', 'Pinot Noir', 'Chardonnay', 'Sauvignon Blanc', 'Pinot Gris', 'Riesling')
data_area <- data_area %>% 
  mutate(common_8_or_not = ifelse(variety %in% common_8_wine, 'common_8', 'not_common_8'))

# check the distribution after grouping
data_area %>% 
  group_by(common_8_or_not) %>% 
  dplyr::summarize(count = n(), High = sum(above90 == 'High'), Low = sum(above90 == 'Low')) %>% 
  arrange(desc(count))
```

# Formal analysis with glm

We will build many logistic regression model in this section

## Area models

In this section we will try to fit model using area v.s. response

We also examined the effect of each region on the response separately relative to the others, for example, compare with non-EastEU region, the wine produced in EastEU may have less probability to be mark above 90 points.

```{r model for every area}
model_Area <- glm(above90 ~   Area  , data = data_area, family = binomial(link = "logit"))

model_Area %>% 
  summary()
```

```{r model_Area_EastEU}
model_Area_EastEU <- data_area %>% 
  mutate(temp_Area = ifelse(Area == 'EastEU', 'EastEU', 'nonEastEU')) %>% 
  glm(above90 ~ 0+temp_Area , data = ., family = binomial(link = "logit"))

model_Area_EastEU %>% 
  summary()
```

```{r model_Area_France}
model_Area_France <- data_area %>% 
  mutate(temp_Area = ifelse(Area == 'France', 'France', 'nonFrance')) %>% 
  glm(above90 ~  temp_Area, data = ., family = binomial(link = "logit"))

model_Area_France %>% 
  summary()
```

```{r model_Area_Italy}
model_Area_Italy <- data_area %>% 
  mutate(temp_Area = ifelse(Area == 'Italy', 'Italy', 'nonItaly')) %>% 
  glm(above90 ~  temp_Area, data = ., family = binomial(link = "logit"))

model_Area_Italy %>% 
  summary()
```

```{r model_Area_Spain}
model_Area_Spain <- data_area %>% 
  mutate(temp_Area = ifelse(Area == 'Spain', 'Spain', 'nonSpain')) %>% 
  glm(above90 ~  temp_Area, data = ., family = binomial(link = "logit"))

model_Area_Spain %>% 
  summary()
```

```{r model_Area_SouthGloble}
model_Area_SouthGloble <- data_area %>% 
  mutate(temp_Area = ifelse(Area == 'SouthGlobe', 'SouthGlobe', 'nonSouthGlobe')) %>% 
  glm(above90 ~  temp_Area, data = ., family = binomial(link = "logit"))

model_Area_SouthGloble %>% 
  summary()
```

```{r model_Area_WestEU}
model_Area_WestEU <- data_area %>% 
  mutate(temp_Area = ifelse(Area == 'WestEU', 'WestEU', 'nonWestEU')) %>% 
  glm(above90 ~  temp_Area, data = ., family = binomial(link = "logit"))

model_Area_WestEU %>% 
  summary()
```

```{r model_Area_NorthAmerica}
model_Area_NorthAmerica <- data_area %>% 
  mutate(temp_Area = ifelse(Area == 'NorthAmerica', 'NorthAmerica', 'nonNorthAmerica')) %>% 
  glm(above90 ~ temp_Area, data = ., family = binomial(link = "logit"))

model_Area_NorthAmerica %>% 
  summary()
```

```{r model_Area_SouthAmerica}
model_Area_SouthAmerica <- data_area %>% 
  mutate(temp_Area = ifelse(Area == 'SouthAmerica', 'SouthAmerica', 'nonSouthAmerica')) %>% 
  glm(above90 ~ temp_Area, data = ., family = binomial(link = "logit"))

model_Area_SouthAmerica %>% 
  summary()
```


## Year models

In this section, we check how year v.s. response 


```{r model_year}
model_year <- data_area %>% 
  drop_na(year) %>% 
  mutate(year = as.numeric(year)) %>% 
  glm(above90 ~  year  , data = ., family = binomial(link = "logit"))

model_year %>% 
  summary()
```

```{r model_log_year}
model_log_year <- data_area %>% 
  drop_na(year) %>% 
  mutate(year = as.numeric(year)) %>% 
  mutate(log_year = log(year)) %>% 
  glm(above90 ~  log_year  , data = ., family = binomial(link = "logit"))

model_log_year %>% 
  summary()
```

we find out the regression coefficients in both case is not significance

## Variety model

In this section, we check how variety v.s. response

```{r model_variety_ori}
# this is a test model using the original 171 varieties, it will produce 171 coefficients
model_variety_ori <- data_area %>% 
  glm(above90 ~ variety  , data = ., family = binomial(link = "logit"))

# model_variety_ori %>% 
#   summary()
```


```{r model_variety}
model_variety <- data_area %>% 
  glm(above90 ~ common_8_or_not  , data = ., family = binomial(link = "logit"))

model_variety %>% 
  summary()
```

We can see that if other factors are not considered, the probability of scoring greater than 90 for 8 common wines is higher than other wines

## Price model

In this section we study the effect of wine price on ratings

```{r model_price}
model_price <- data_area %>% 
  drop_na(price) %>% 
  glm(above90 ~ price  , data = ., family = binomial(link = "logit"))

model_price %>% 
  summary()
```

since we have some wines with very high price, we perform a log transform on price

```{r model_log_price}
model_log_price <- data_area %>% 
  drop_na(price) %>% 
  mutate(log_price = log(price)) %>% 
  glm(above90 ~ log_price  , data = ., family = binomial(link = "logit"))

model_log_price %>% 
  summary()
```

As the price of a wine increases, so does the probability of it being rated 90+


## Winery model

Now we examine the effect of winery size on a wine's score point

```{r model_winery}
model_winery <- data_area %>% 
  drop_na(processed_winery) %>% 
  glm(above90 ~ processed_winery  , data = ., family = binomial(link = "logit"))

model_winery %>% 
  summary()
```

Larger wineries are more likely to score above 90 than smaller wineries.

## Full model

Now we fit a full model for all variables

```{r full model}
data_full <- data_area %>% 
  drop_na() %>% 
  mutate(year = as.numeric(year)) %>% 
  mutate(log_price = log(price))  
  
model_full <- glm(above90 ~ log_price + year + processed_winery + common_8_or_not + Area , data = data_full, family = binomial(link = "logit"))

model_full %>%
  summary()
```

The coefficients of year, price, and winery are significant, but the coefficients of variety and some regions are not significant. We will use stepwise regression to continue the study.

```{r stepwise regression}
stepAIC(model_full,direction="both")
```

According to the AIC criterion, we discard variety and continue modeling with the remaining four variables.

```{r model_without_variety}
model_without_variety <- glm(above90 ~ log_price + year + processed_winery + Area , data = data_full, family = binomial(link = "logit"))

model_without_variety %>%
  summary()
```

The coefficient for year is no longer significant, we try to remove the year and continue modeling

```{r model_without_variety_year}
# same as finally for now
model_without_variety_year <- glm(above90 ~ log_price + processed_winery + Area , data = data_full, family = binomial(link = "logit"))

model_without_variety_year %>%
  summary()
```

If we start our full model by drop year since it not significant when modeling year v.s. response, we get a same model dropping year and variety 

```{r model_without_year}
model_without_year <- glm(formula = above90 ~ log_price + common_8_or_not + processed_winery +  Area, 
    family = binomial(link = "logit"), data = data_full)

model_without_year %>% 
  summary()

step(model_without_year)
```

Now we achieve our finally model:

$$
\widehat{above90} = \widehat{\beta_0} +\widehat{\beta_1} \cdot log(x_{price}) + \widehat{\beta_2} \cdot \mathbb{I}_{winery}(x_{winery})+ \sum_{i=3}^{9}\widehat{\beta_i} \cdot \mathbb{I}_{Area_i}(x_{Area_i}) 
$$
where:
$$
\mathbb{I}_{\mbox{winery}}(x_{winery})=\left\{
\begin{array}{ll}
1 ~~~ \mbox{if winery of} ~ x \mbox{th observation is small winery},\\
0 ~~~ \mbox{Otherwise}.\\
\end{array}
\right.
$$

$$
\mathbb{I}_{{Area_i}}(x_{Area_i})=\left\{
\begin{array}{ll}
1 ~~~ \mbox{if area of} ~ x \mbox{th observation is ith area},\\
0 ~~~ \mbox{Otherwise}.\\
\end{array}
\right.
$$


```{r model_final}
model_final <- glm(formula = above90 ~ log_price + processed_winery +  Area, 
    family = binomial(link = "logit"), data = data_full)

model_final %>% 
  summary()
```

We can group those that do not belong to Western European countries and get some summative pictures

```{r model_final_EU}
model_final_EU <- data_full %>% 
  mutate(temp_Area = ifelse(Area == 'WestEU', 'WestEU', 'nonWestEU')) %>% 
  glm(above90 ~ temp_Area + processed_winery + log_price  , data = ., family = binomial(link = "logit"))
```


```{r model_final_EU plots}
plot_model(model_final_EU,type="pred",terms=c("log_price", "temp_Area", "processed_winery"))

plot_model(model_final_EU,type="pred",terms=c("log_price", "temp_Area"))

plot_model(model_final_EU, show.values=TRUE)

# plot_model(model_final, show.values=TRUE)
```


# Model checking and diagnostics for logistic regression

## Deviance

```{r check deviance}
(2110.3-1511.4) > qchisq(0.95, df=1791-1782)
```

The final model is significantly different from the null model.

## Hosmer-Lemeshow goodness 

```{r Hosmer-Lemeshow goodness, warning=FALSE}
source(url("http://www.chrisbilder.com/categorical/Chapter5/AllGOFTests.R"))
for (i in 6:10){
  print(HLTest(model_final, g=i))
}
```

At different values of g, our model sometimes shows lack of fit, which means that our model may not fit the response variable well

## Multicollinearity

Variance inflation factor (VIF) is an effective method to check for direct multicollinearity of variables, but VIF is designed for numerical variables and cannot be used for categorical variables, and we initially tried manually generating dummy variables from categorical variables to calculate VIF. But then we found that the VIF function in the 'car' package contains GVIF, which can be used to handle categorical variables

```{r car vif}
car::vif(model_full)

car::vif(model_final)
```

From the results, there is no multicollinearity among the variables in our full and final models.

```{r VIF using dummy variables}
# data_dummy <- dummy_cols(data_full, select_columns = c('processed_winery', 'Area', 'common_8_or_not')) %>% 
#   dplyr::select(-c('processed_winery_small wineries', 'common_8_or_not_not_common_8', 'Area_WestEU'))
# 
# model_dummy <- data_dummy[1:1792 ,c(10, 15,16,18:26)] %>% 
#   glm(above90 ~ ., data = .,family = binomial(link = "logit"))
# 
# model_dummy %>% 
#   summary()
# 
# vif(model_dummy)
# 
# model_dummy_final <- data_dummy[1:1792 ,c(10, 15,18:25)] %>% 
#   glm(above90 ~ ., data = .,family = binomial(link = "logit"))
# 
# model_dummy_final %>% 
#   summary()
# 
# vif(model_dummy_final)
# 
# 
# model_dummy_without_NorthAmerica <- data_dummy[1:1792 ,c(10, 15,18:25)] %>%
#   filter(Area_NorthAmerica != 1) %>% 
#   dplyr::select(-'Area_NorthAmerica') %>% 
#   glm(above90 ~ ., data = .,family = binomial(link = "logit"))
# 
# model_dummy_without_NorthAmerica %>% 
#   summary()
# 
# vif(model_dummy_without_NorthAmerica)
```

## Classification ability

Although our main question is to investigate what is the variable that affects whether the score is greater than 90, because of our logistic regression model for a binomial response variable, our model can be used as a classifier to judge a given information Whether the wine score is greater than 90. So we use the receiver operating characteristic (ROC) curve and area under the ROC curve (AUC) value to assess the predictive power of our model

```{r ROC}
predict <- predict(model_final, data_full, type="response")
above90labels <- ifelse(data_full$above90 == "High", 1, 0)
score <- prediction(predict,above90labels)
perf <- performance(score,"tpr","fpr")
auc <- performance(score,"auc")
perfd <- data.frame(x= perf@x.values[1][[1]], y=perf@y.values[1][[1]])
ROCplot<- ggplot(perfd, aes(x= x, y=y)) + 
  geom_line() +
  xlab("False positive rate") +
  ylab("True positive rate") +
  ggtitle(paste("Area under the curve:", round(auc@y.values[[1]], 3)))+
  theme(title=element_text(size=15),axis.text.x = element_text(size=15),axis.text.y = element_text(size=15),legend.text = element_text(size=15))
ROCplot
```

The area under the curve is about 0.85, which is reasonable considering that we make many grouping on our variables. 
The effect of classification is acceptable and not bad.


# Conclusion

After the overall analysis, we can get the conclusion. The wines’ points are influenced by price, wineries and areas. Here, the probabilities of getting high score in west Europe is significantly different from other areas. Wines’ varieties can affect the score if we consider it separately, however, combining with other factors, varieties are not so obvious to influence the scores.

# Future work

## classification tree

In the previous model chapter we used our logistic regression model as a classification algorithm and plotted the ROC to examine the classification effect. Going a step further, we can try to use the classification tree algorithm to obtain a classification model to meet possible classification needs. Of course, when building the tree we need to first segment our numerical variables

## Analysis at a finer geographic level

We deduce the origin of wine by country and province labels in the dataset, in fact we are doing research almost at the continent level. For some regions with vast areas or large differences in production areas, a more detailed division of production areas will be more reasonable.

## Grouping method

We have grouped categorical variables with too many levels when processing the data. The method of grouping is relatively subjective. Although we have considered many grouping methods, and we show the most reasonable grouping method here, there may be more Good grouping we didn't consider, it might be helpful to know more background about wine.

## Model selection

We selected models based on AIC criteria only, BIC and some other criteria should probably be considered.

## Other way to divied wine's point

We count wines with a score greater than 90 as high-quality wines and those below 90 as low-quality wines, but in fact this is a very subjective segmentation, and we should use a more reasonable segmentation to distinguish the quality of the wine.

We divide the wine score into whether it is greater than 90, but in fact we have a numerical score for the wine, maybe we can try a linear model

# Table plots for PPT

```{r model_final_changed_area_base}

data_full$Area_based_on_WestEU <- fct_relevel(data_full$Area, c('WestEU','NorthAmerica','Italy','France','Spain','SouthAmerica','SouthGlobe','EastEU'))

model_final_changed_area_base <- glm(formula = above90 ~ log_price + processed_winery +  Area_based_on_WestEU, 
    family = binomial(link = "logit"), data = data_full)

model_final_changed_area_base %>% 
  summary()

```


```{r model_area_changed_area_base}

temp_data<-data_full
temp_data$Area <- fct_relevel(temp_data$Area, c('WestEU','NorthAmerica','Italy','France','Spain','SouthAmerica','SouthGlobe','EastEU'))

model_area_changed_area_base <- glm(formula = above90 ~ Area, 
    family = binomial(link = "logit"), data = temp_data)

model_area_changed_area_base %>% 
  summary()

```

```{r plot for regression tables for PPT}
tab_model(model_final, digits = 5,transform = NULL, show.r2 = FALSE, show.dev = TRUE)
tab_model(model_Area, digits = 5,transform = NULL, show.r2 = FALSE, show.dev = TRUE)
tab_model(model_price, digits = 5,transform = NULL, show.r2 = FALSE, show.dev = TRUE)
tab_model(model_variety, digits = 5,transform = NULL, show.r2 = FALSE, show.dev = TRUE)
tab_model(model_winery, digits = 5,transform = NULL, show.r2 = FALSE, show.dev = TRUE)
tab_model(model_year, digits = 5,transform = NULL, show.r2 = FALSE, show.dev = TRUE)
tab_model(model_without_year, digits = 5,transform = NULL, show.r2 = FALSE, show.dev = TRUE, show.aic = TRUE)
tab_model(model_final_changed_area_base, digits = 5,transform = NULL, show.r2 = FALSE, show.dev = TRUE, show.aic = TRUE)
tab_model(model_area_changed_area_base, digits = 5,transform = NULL, show.r2 = FALSE, show.dev = TRUE)
```




